A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-09-06 pilot-publication/manuscript.Rmd
Add ethics from PGI Chandigarh

## Ethics and Dissemination
We were granted research ethics approval from each participating
hospital. The approval numbers were IEC(II)/OUT/134/2022 for King
Edward Memorial Seth G. S. Medical College and K.E.M. Hospital,
Mumbai; IEC/214/22 for Lokmanya Tilak Municipal Medical College and
General Hospital, Mumbai; HBTMC/266/SURGERY for HBT Medical College
And Dr. R N Cooper Municipal General Hospital, Mumbai;
CREC/2022/FEB/1(ii) for Medica Superspecialty Hospital, Kolkata;
Medical College Kolkata, Kolkata; NRSmC/IEC/93/2021 for Sir Nil Ratan
Sircar Medical College & Hospital, Kolkata; XXX for Postgraduate
Institute of Medical Education & Research, Chandigarh.

>>>>

## Ethics and Dissemination
We were granted research ethics approval from each participating
hospital. The approval numbers were IEC(II)/OUT/134/2022 for King
Edward Memorial Seth G. S. Medical College and K.E.M. Hospital,
Mumbai; IEC/214/22 for Lokmanya Tilak Municipal Medical College and
General Hospital, Mumbai; HBTMC/266/SURGERY for HBT Medical College
And Dr. R N Cooper Municipal General Hospital, Mumbai;
CREC/2022/FEB/1(ii) for Medica Superspecialty Hospital, Kolkata;
Medical College Kolkata, Kolkata; NRSmC/IEC/93/2021 for Sir Nil Ratan
Sircar Medical College & Hospital, Kolkata; and PGI/IEC/2022/000/003
for Postgraduate Institute of Medical Education & Research,
Chandigarh.
